---
title: "Youtube Streamers Analysis"
author: "Aatish"
date: "2023-12-16"
output: html_document
---
### Aim:
To Perform a comprehensive analysis of the dataset to extract insights about the top YouTube content creators.

Install & load required Libraries
```{r message=FALSE, warning=FALSE}
install.packages("tidyverse",repos="https://cloud.r-project.org/")
library(tidyverse)
install.packages("skimr",repos="https://cloud.r-project.org/")
library(skimr)
install.packages("ggcorrplot",repos="https://cloud.r-project.org/")
library(ggcorrplot)
install.packages("googledrive",repos="https://cloud.r-project.org/")
library(googledrive)
```
Load Dataset from Google Drive
```{r fig.width=14, message=FALSE, warning=FALSE}
mydrive <- drive_find(n_max = 10) #this will direct your gdrive browser for permission
id <- "1TRPPHAA2nn2NtpHn5GZaxKYVKzj27jQ5"
youtube_df <- read.csv(paste0("https://drive.google.com/uc?id=",id,
                              "&export=download"),na.strings = c(""))
as_tibble(head(youtube_df,10))
```
### Data Exploration
```{r fig.width=14}
skim_without_charts(youtube_df)
```
As we can see there are only 994 distinct values in dataset so remove duplicate rows
```{r}
youtube_df <- youtube_df[!duplicated(youtube_df$Username),]
```
Check for Missing Values
```{r fig.width=14}
colSums(is.na(youtube_df))
```
Replace missing values with **Entertainment**
```{r}
youtube_df$Categories <- youtube_df$Categories %>%
  replace_na('Entertainment')
```
Check Missing values
```{r}
colSums(is.na(youtube_df))
```
Rename Column name to **Subscribers**
```{r}
youtube_df <- rename(youtube_df, Subscribers = Suscribers)
```

```{r}
top100_categories <- head(youtube_df,100)
top100 <- top100_categories%>%
  group_by(Categories)%>%
  summarise(no_of_streamer = n())%>%
  arrange(-no_of_streamer)
print(top100)
```
## Trend Analysis
```{r}
ggplot(data = top100, aes(no_of_streamer,reorder(Categories,no_of_streamer)))+
  geom_col(fill="purple")+
  labs(title = "Top Categories Among Top Streamers",caption="Taking Top 100 Streamers",x="No. of Streamer",y="Categories")
```
```{r fig.height=4, fig.width=6}
#Creating Correlation Matrix
new_youtube_df <- top100_categories %>%
  group_by(Categories) %>%
  summarise(Total_Subscribers = sum(Subscribers), Total_Likes = sum(Likes),
            Total_Comments = sum(Comments), Total_Visits = sum(Visits))%>%
  arrange(-Total_Subscribers)
cor_matrix <- cor(new_youtube_df[sapply(new_youtube_df,is.numeric)])
print(cor_matrix)

#Creating a heatmap to visually understand the structure
ggcorrplot(cor_matrix, method = "square",lab = TRUE)
```




## Audience Study
```{r}
#Analyse the distribution of streamers audience by country and Group the data by country & content category
country_categories <- youtube_df %>%
  group_by(Country,Categories)%>%
  summarise(Total_visits = sum(Visits), Total_Likes = sum(Likes),
            Total_Subscibers = sum(Subscribers),.groups = "drop")
```
```{r fig.height=8, fig.width=14}
#Create a scatterplot to visualize the distribution of content categories by country
ggplot(data = country_categories)+
  geom_point(aes(Categories,Country))+
  theme(axis.text.x = element_text(angle = 90))+
  labs(title = "Distribution of Content Categories by Country",x="Categories",
       y="Country")
```


## Performance Metrics
```{r}
#Calculate average metrics
avg_matrices <- youtube_df %>%
  group_by(Categories) %>%
  summarise(Avg_Subscribers = mean(Subscribers), Avg_Likes = mean(Likes),
            Avg_Comments = mean(Comments), Avg_Visits = mean(Visits))
```
```{r fig.height=4, fig.width=6}
#Checking pattern & anomalies
avg_cor <- cor(avg_matrices[sapply(avg_matrices,is.numeric)])
round(avg_cor,2)
ggcorrplot(avg_cor,method = "square",lab = TRUE,title = "Performance Matrix")
```
```{r}
#top10 categories by Likes
top10_L <- head(arrange(avg_matrices,-Avg_Likes),10)
ggplot(data = top10_L,mapping = aes(Avg_Likes,reorder(Categories,Avg_Likes)))+
  geom_col(fill="pink")+
  labs(title = "Top 10 Categories by Likes", x ="Avg Likes", y ="Categories")
```
```{r}
 #Top10 Categories by Comments
top10_C <- head(arrange(avg_matrices,-Avg_Comments),10)
ggplot(data = top10_C, mapping = aes(Avg_Comments,reorder(Categories,Avg_Comments)))+
  geom_col(fill="skyblue")+
  labs(title = "Top 10 Categories by Comments", x ="Avg Comments", y ="Categories")
```



## Content Categories
```{r}
#Count number of Streamers in each category
Content_cat <- youtube_df %>%
  group_by(Categories)%>%
  summarise(No_of_Streamer = n())
arrange(Content_cat,-No_of_Streamer)
```
```{r fig.height=6, fig.width=14}
#Create a horizontal bar chart to visualize the distribution of content categories
ggplot(data = Content_cat, mapping = aes(reorder(Categories,-No_of_Streamer),No_of_Streamer))+
  geom_col()+
  theme(axis.text.x = element_text(angle = 90))+
  labs(title = "Distribution of Content Categories", x ="Categories", y ="No of Streamers")
```



## Brands & Collboration
```{r}
#creating proxy performance matrix 
per_matrix <- youtube_df%>%
  mutate(Brand_collab = Likes+Comments+Visits+Subscribers)
top10_streamer <- head(arrange(per_matrix,-Brand_collab),10)
```
```{r}
ggplot(data = top10_streamer, aes(Brand_collab,reorder(Username,Brand_collab)))+
  geom_col(fill="light green")+
  labs(title = "Top Streamer for Brand Collaboration",x="Performance(Proxy)",
       y="Top Streamer")
```

## Benchmarking
```{r}
#calculating mean values of subscribers,visits,likes & comments

a <- mean(youtube_df$Subscribers)
b <- mean(youtube_df$Visits)
c <- mean(youtube_df$Likes)
d <- mean(youtube_df$Comments)

above_avg_streamer <- filter(youtube_df, Subscribers >a & Visits > b & Likes > c
                             & Comments > d)
print(select(above_avg_streamer,Username,Subscribers,Visits,Likes,Comments))
```
## Content Recommendation for Users
```{r}
#take input from user
var1 <- readline("Search by Categories:")
#for now take input as "Entertainment"
var1 <- "Entertainment"
```
```{r message=FALSE, warning=FALSE}
#Recommended User based on input
for (i in 1:nrow(above_avg_streamer))
{
cat <- above_avg_streamer[i,3]
if(str_detect(cat,var1))
{
  u_name <- above_avg_streamer[i,2]
  print(u_name)
}
}
```
## Close Competitor among Streamers
```{r}
#Taking input frome user
var <- readline("search username:")
```

```{r}
#for now take any username 
var <- "CoComelon"
```

```{r}
k <- youtube_df$Username
j <- which(k == var)
l <- youtube_df[j,3]
m <- youtube_df[j,4]
filtered_data <- filter(youtube_df, Categories == l)
num <- numeric()
```

```{r}
for (i in 1:nrow(filtered_data)) {
  sub <- filtered_data[i,4]
  x <- abs(sub - m)
  num <- c(num,x)
}
y <- which.min(num)
print(paste("Close Competitor of", var, "is",(filtered_data[(y+1),2])))
```





